\documentclass{article}

\textheight = 600pt

\pagestyle{empty}

\begin{document}

\section*{Assignment 3: The Shooter}

\subsubsection*{Spine}

\subsubsection*{Synopsis}

\begin{enumerate}

  \item Where are we; where/when does the story take place?

  \item Who are we following in the story (the protagonist) and why them?

  \item Who or what force is opposed to the hero of the story, and why are they
    in opposition (the antagonist)?

  \item What do these characters want to accomplish; what is at stake for them?

  \item What is the ensuing conflict, and why does it exist?

  \item How does the action rise; how do things get more tense?

  \item What is the final crisis, and how does it play out?

  \item How do things resolve and wrap up?

\end{enumerate}

The events are happening in the future, year 2337. We are on the first colonial
spaceship ``Expeditioner'' on the interplanetary journey. Jake is being released
from the brig after being falsely accused of the attack resource compartment of
the ship. Remembering his talent and skills the military commanders decided to
give him a chance of rejoining the spaceship defenders fleet. Jake has to go
through a series of challenges and is given a simple hoverboard and a harmless
laser gun to be able to begin.

Jake meets his old friend Cillian who warmly welcomes him and says that he
always believed Jake to be innocent but no one was listening when he tried to
defend Jake. Cillian now has an eight year old daughter Ann, very curious and
willing to take her father path of spaceship defender. Jake meets Ann and
becomes her friend, he sees a great potential in this little swifty.

Jane learns that Jake is back on his way to the defenders fleet and argues with
the commanders why Jake was given this impossible chance, but they quickly
expained that she is not yet the commander and they know better who deserves to
be given a second chance.

Jake starts his tests with shooting dummy targets in the practice area. He
quickly gains the control over the hoverboard and hitting the targets, which
appear for few seconds, is not something for him to worry about. The next level
is more challenging, Jake has no control over the hoverboard but someone else
does and that happens to be Jane. However, with utmost strain Jake manages to
pass this test and regaining the control over the hoverboards gracefully moves
to next chamber where he is given a heavy blaster to practice destroying
machinery. This test appears to be relatively easy, the years in the brig gym
were not in vain.

The following day is the resting day for Jake and he spends it together with
Cillian and Ann when they devise a plan how to extract documents from one of the
drawers in Jane's room. Jake will tease Jane to make her go after him on her
scooter while Cillian and Ann will be retrieving the papers.

Next day Jake demonstrates how perfectly he controls the scooter while
performing the maneuvering test among dummy space mines. After that he is to
perform the last test, shooting the mines and maneuvering. Jane decides to go
after Jake with her devious plan to drive him towards coming asteroids. They
have an intense chase during which they both demonstrate elegant and skillful
methods of avoiding and destroying dummy mines until they disappear far from the
spaceship. The only one who felt it a danger was Jake's father, who was silently
following the spaceship and decided to follow the racers. Meanwhile, Jane
started to shoot at Jake's scooter causing shaking inside and minor damage. Jake
began taking dodgy curves avoiding perilous rays from Jane's scooter guns. He
manages outmaneuver her and appear behind her. With knowledge about scooters and
careful measurement Jake shoots at her scooter disable its engine and guns
making her helpless. Jane realizes that her uncontrollable scooter flies towards
a big asteroid at high speed. At this moment Jake's father gains on them and
seeing what dreadful fate awaits the scooter with its pilot decides to go full
throttle. Being just in time he points the guns of this pirate vehicle at the
asteroid and with deafening sound cracks the great stone into several pieces
allowing Jane's scooter go through safely. After that he uses the magnet gun to
attach her scooter on his vehicle and safely delivers her with his son Jake
peacefully flying next to him.

When they arrive the are met with the commanders, Cillian, Ann and the captain
of ``Expeditioner''. The commanders hold the papers which Cillian gave to them
and they escort Jane to the brig where she will spend at least 20 years. Jake
has his reputation restored and has good chances to become a commander, though
he personally thinks to help Cillian to train Ann to be an outstanding defender
and would prefer to be an advisor for the commanders when he retires.

Jake's father and spaceship captain part again at this moment with warm feelings
and sly smiles on their faces. ``Expeditioner'' continues its course to the
worlds where we are going to settle and develop our civilization.

\subsubsection*{Characters Briefs}

\begin{enumerate}

  \item Who is he/she? Are they a primary or secondary character and how do they
    relate to the game story?

  \item What do they look like? What are they wearing or carrying with them?

  \item What is their personality like and how does that personality help
    fulfill their role in the game story?

  \item How do they relate to other characters in the game?

  \item What are their strengths and weaknesses, and how can that affect the game story?

  \item What are the motivating character goals for this character?

\end{enumerate}

\subsubsection*{Jake}

\begin{itemize}

  \item Former space pirate was offered a job as a defender of the spaceship;

  \item His father is the captain of a small pirate space fleet and mother is a
    scientist on Earth studying rare minerals;

  \item He has been progressively excelling with his skills as a shooter
    defender and aiming for a position of the commander of their defender fleet;

  \item After five years of being a defender he has been framed for the attack
    on the resource compartment and locked in the brig for ten years;

  \item While working out in the brig gym was planning on getting back his
    reputation after release;

  \item He is not very tall, around 1.7 meter, sinewy, well trained and visually
    attractive physique with prominent muscles;

  \item Dark, almost black short hair, fair complexion with piercing look of
    blue eyes, however, charming smile;

  \item He likes to take care of his body, always accurate nails, clean hands
    and face, pleasant scent, though does not like formal suits;

  \item Wears dark green with aurulent stripes suit of sportwear style and
    lightweight sneakers of straw color;

  \item Since childhood has been nimble, with quick reflexes. Has been showing
    interest towards exploration of new territories, thus joined his father's
    pirate fleet for travelling to nearby planets, mostly Mars, collecting rare
    minerals and giving them to his mother for her research secretly from his
    father, who was selling the minerals on the black market in order to make
    money for good living and fleet maintenance;

  \item Mother has always seen good tendency in her son on his way of growing up
    despite the fact of joining the pirates and proved to be right when he joined
    the defenders fleet of ``Expeditioner'';

\end{itemize}

Jake is the protagonist in our game.

In his childhood has been constantly showing interest towards exploration of new
territories which later led him to joining father's small pirate space fleet for
travelling to nearby planets (mostly Mars, though), collecting rare minerals and
giving them to his mother who is a scientist on Earth studying rare minerals.
Jake did so secretly from his father --- space pirate captain --- who was
selling minerals on the black market for good living and space vehicles
maintenance.

Military forces have always been watching pirates constantly looking for the
brilliant ones. It happened that they offered a well paid job as defenders of a
spaceship to several pirates, among which were Jake and his father. Father and
few others refused the offer, however, Jake and his friend Cillian decided to
take the offer because for them it was a great chance to travel to new worlds
and explore the unknown. Jake's mother was proud of his talented son, she has
always seen good tendency in him on his way of growing up despite the fact of
joining the pirates Jake proved her right.

Jake has been progressively excelling with his skills as a shooter defender and
aiming for a higher position in the defender fleet and after five years has been
framed for the attack on the resource compartment and locked in the brig for ten
years. While staying locked Jake was working out in the brig gym and planning on
getting his reputation back. Being a smart and nimble man with quick reflexes he
easily conceived who was in charge of his exile as well as no one would listen
to him after the release, though he might count on Cillian.

Later Jake learns that his father with his fleet were following ``Expeditioner''
all this time because they decided to take their chances for discovering new
unknown minerals and because his father and the spaceship captain are old
military academy friends but chose different paths.

Jake is not very tall, roughly 1.7 meter, sinewy and well trained not without
the help of ten years in the brig. His attractive physique with prominent
muscles have been always fancied by his female comrades. He has dark, nearly
coal black short hair and fair complexion with piercing look of blue eyes. He
has been an open boy since the childhood and often smiles kindly towards people
getting them on the right side.

\subsubsection*{Dead--Eye Jane}

\begin{itemize}

  \item Antagonist;

  \item Has been grown by her father hunter, her mother has left them for
    another man (scientist?);

  \item In the childhood has learnt about hunting; could shoot a hare into the
    eye from a hundred meters thus received the nickname;

  \item Was offered a place among spaceship defenders during studies in the
    military academy;

  \item Noticed to have an ability to manipulate boys due to her natural beauty
    and charming smile, developed greed for power;

  \item Long (ends just below her scapulae) amber straight hair; fresh and
    healthy looking light face; celestial shape nose; large eyes change color
    from hazel to green depending on mood and lighting; the trained body is well
    proportioned and attractive;

  \item Wears black long knee--high boots, olive drab trousers and jacket made
    of high--tech textile; tangerine color shirt with orchid color neck tab;
    white leather gloves;

  \item Her laser and blaster guns, as well as the hoverboard and space scooter,
    are colored in the same manner: white color with amber color skewed stripes;

  \item Does not use make up except for scarlet lipstick; usually braids her
    hair in ponytail style;

  \item Rather social and sly, prefers to have things her way and be an
    authority;

\end{itemize}

Dead--Eye Jane is the antagonist.

She was raised by her father hunter since her mother left them for a
mathematician. She was joining her father in his game hunting discovering a
talent for marksmanship and excelling at shooting being able to hit a hare in
the eye from a hundred meters thus receiving the nickname. Jane went to the
military academy where she has proved to be an excellent fighter and been
offered a place among spaceship defenders.

She likes to take care of her long straight amber hair which she braids in a
ponytail style. Jane has healthy and fresh looking light face with celestial
shape nose and large eyes whose color change from hazel to green depending on
mood and lighting. She has always been social and during her studies noticed to
have an ability to manipulate boys due to her natural beauty and charming smile.
She did not use make-up but started to use crimson lipstick to intensify her
values and become more confident. Jane learned to be very sly preferring to have
things her way and being an authority, gradually developing a greed for power.

She has met Jake in the defenders fleet already being in high ranks and aiming
for the captain position. Jane started to feel danger for her goal since Jake
was getting well appraised by the military commanders and Jane has organized an
attack on the ``Expeditioner'' resource compartment making everyone believe Jake
to be responsible.

She wears a tangerine color shirt with orchid color neck tab and olive drab
jacket and trousers made of high--tech textile sewn to be comfortable and not
hampering her movements. Her black long knee--high boots and white leather
gloves add an elegant look to her outfit.

Her laser and blaster guns, as well as the hoverboard and space scooter, are
colored in one manner: white color with amber color skewed stripes.

\subsubsection*{Setting Description}

\begin{itemize}

  \item Shooting in the Space;

  \item The events take place in future, say, 2337. Interplanetary travels start
    to develop into massive process, launching the first colonial spaceship
    ``Expeditioner'';

  \item The spaceship was built in the space, the parts being delivered by space
    trucks, otherwise it would be impossible to launch such a massive structure
    to the space;

  \item Colonial spaceship is a formidable construction providing life support
    to half a million population with currently around 100 thousand people with
    expectation to have the population grow over the course of the journey;

  \item The spaceship is painted mostly in dark grey and dark blue colors with
    white stripes in several places;

  \item The ship is equipped with many middle size salvage spacecrafts as well
    as with a great number of machine guns, laser blasters and other defensive
    weaponry. From the outside the spaceship has a resemblance of a military
    cruiser with a more flat bilge;

  \item The ship is using artificial gravity;

  \item Skilled pilots defend the ship from possible danger outside;

  \item Laser shooting in a spaceship shooting practice area;

  \item Spacious area separated into two halves:

    \begin{enumerate}

      \item The sector where the shooters start, surfaces are colored with
        green and silver, rich blueish light;

      \item The sector where the dummy targets appear, surfaces are metal grey
        with target zones colored as red with black stripe pattern, generally
        dim, target zones are illuminated using spot lighting;

    \end{enumerate}

  \item The target zones are located in the floor and ceiling as disks with
    sliding shutters, and in the walls as sliding doors from which the dummy
    enemies appear for a few seconds;

  \item The shooters are on hoverboards, moving in the green area. Next level, the
    hoverboards are moving randomly with shooters having to keep balance and
    shoot;

  \item Blaster shooting practice to destroy or disable heavy machinery;

  \item Located in the old depot of the spaceship where destroyed and unwanted
    machinery is kept. These old and damaged vehicles are used for blaster
    shooting practice and equipped with sensors for detecting successful hits.
    The shooters use heavy slow but devastating blaster weapons;

  \item Shooting dummy targets in the open space using space scooters. These
    vehicles have an egg shape with roughly one third of the carcass made of
    adamant transparent material providing the front, side and top view for the
    pilot. Inside, the control system has access to four cameras installed on
    the rear, bottom, left and right sides. A scooter can be equipped with
    different guns, depending on the task, but always on the sides of the
    vehicle and can be tilted for aiming only in the vertical plane. For
    horizontal adjustment the pilot has to turn the scooter;

  \item The shooters are divided into two teams, one team flies on scooters and
    the other remotely controls dummy targets equipped with visual systems and
    harmless weapons. The scooters take off from the starting platform and for
    the purpose of this exercise are also equipped with harmless weapons. The
    successful strikes are detected using special sensors;

  \item Shooting/maneuvering space obstacle mines while on scooters. These mines
    are made of cheap expendable material;

  \item If the task is to destroy the mines the scooters are equipped with laser
    guns. Therefore, it is also important not to cause any friendly fire to the
    other shooters. Although, these laser guns will not destroy a scooter they
    may cause certain damage to the vehicle.

  \item If the task is to avoid the mines using maneuvering skills then the
    scooters fly with no guns installed;

\end{itemize}

\end{document}
