\documentclass{article}

\textheight = 600pt

\pagestyle{empty}

\begin{document}

\section*{Assignment 2: Movie ``Inception''}

\subsubsection*{Spine}

A great expert in subconscious infiltration is hired to break the energy
monopoly conglomerate and assembles his team for the task. They exploit the idea
of dream within a dream to go down several layers of sleeping in order to seed
the idea of dissolving a company into the brain of the company owner's son.

\subsubsection*{Synopsis}

\begin{enumerate}

  \item Where are we; where/when does the story take place?

  \item Who are we following in the story (the protagonist) and why them?

  \item Who or what force is opposed to the hero of the story, and why are they
    in opposition (the antagonist)?

  \item What do these characters want to accomplish; what is at stake for them?

  \item What is the ensuing conflict, and why does it exist?

  \item How does the action rise; how do things get more tense?

  \item What is the final crisis, and how does it play out?

  \item How do things resolve and wrap up?

\end{enumerate}

We see a man (Dom Cobb) washed ashore and weakly looking at two children just a
moment before fainting away. He is discovered by two armed men and dragged to a
Japanese style house where he is met with and old man who looks at the man's
belongings and sees a brass spinner.
We learn that the two men may have certain things in common and the brass
spinner might have a meaning.

We see Dom and his partner (Arthur) performing a unique form of corporate
espionage by infiltrating the subconscious of their target (Saito) in the two
layers of dreams thus extracting precious information. We see them in the dream
worlds before they wake back to our contemporary world. We also learn that Dom's
wife Mal is trying to sabotage the work Dom and Arthur are doing thus arguably
appear to be the antagonist.

We learn that Dom has become a fugitive and a subject of refusal to entry the
United States due to the past unfortunate events. Saito approaches him with an
offer to help Dom to clear his criminal records and chance to reunite with his
children in exchange for an extremely difficult and delicate job: plant an idea
into a specific person's mind. This person is Robert Fisher, the son of Maurice
Fisher who is the owner of large energy conglomerate and Saito's competitor and
the idea is to dissolve father's company.

We follow the main character as he assembles his team with an architect
(Ariadne), forger (Eames) and chemist (Yusuf) as well as escaping from goons who
were hired to get Dom to the previous employer for failing extracting the secret
from Saito. We learn that every member of a team should have a totem which is
used to help the owner to perceive whether he/she is in someone's dream.

We see that Mal has committed suicide because she believed that the real world is
a dream in the only way to wake up is to die. Dom perpetually blames himself for
her death and that her death is the real reason of charges against him and a
restraining order to see his children.

Whenever Dom wants to sleep he uses a sedative since it is now the only way he
can sleep. Every time he sleeps he sees Mal coming to his dreams and trying to
sabotage his actions.

The main action begins when the team (Dom, Arthur, Saito, Ariadne, Eames and
Yusuf) get a 10--hour flight with Robert in which they use Yusuf's strong
sedative to lure Robert into a long shared dream with three levels which have to
be synchronized with perfect timing in order to succeed.

The first level begins with Yusuf's dream in a city under heavy rain. Here we
learn that Robert's mind has been trained to protect against subconscious
intruders and generated defenders come closer to the team and mortally wound
Saito. Robert is kidnapped and forced to tell a code from his father's safe but
he manages to generate a series of random numbers which are later used in next
levels of dream and they all sit in a van which is driven by Yusuf escaping from
the defending forces of Robert's mind.

The second level is Arthur's dream in a hotel which inherits all gravitational
effects of the driving van from the first level. Here Dom decides to perform a
very dangerous trick --- acting as a mind protection trainer to delude Robert's
mind and lure it to his side. They convince Robert to enter his father's partner
subconscious as his projection confesses that he was behind the kidnapping.

Then all but Arthur go to the next level which appears to be actually Roberts'
dream and supposedly the last level of their plan. They push through their way
to the fortress where the safe is. Since Ariadne has created this level only she
knows the secret passage and Dom forces her to tell because they do not have
enough time and puts the operation in danger due to the chance of Mal's
appearance. Mal indeed appears when the team almost succeeded and shoots Robert
after which Dom shoots Mal. Dom considers a mission failure but Ariadne
convinces him to go into so-called limbo (dream where is no time) to save Robert
and bring him back using defibrillator. While in limbo they appear in the world
which Dom and Mal have built together long time ago and now coming apart. They
find Mal and Dom convinces her that he would stay with her if she tells where
Robert is. Mal reveals his location and Ariadne kicks Robert back to life in
level three where he goes to the room where his dying father is and opens the
safe with the numbers he pronounced in level 1. He finds out the truth that his
father wanted Robert to be his own man and decides to dissolves father's
company. In limbo Ariadne jumps off the building to go back where Eames
initiates the building collapse to be in time for Arthur's kick which in turn to
be in precise timing with Yusuf's kick. However, Dom stayed in limbo to find
Saito who died in level 3 because that Saito is his only chance to reunite with
his children.

That is where we are brought back to the first scene of the movie revealing that
the old man is Saito and Dom has come to try to bring them both back. We see
that Dom wakes up in the plane with everybody woken up and alive, goes through
the customs with no problem and joins his children while leaving his totem
spinning on the table. With that we are left with our assumption whether is was
reality or a dream.

\subsubsection*{Characters Briefs}

\begin{enumerate}

  \item Who is he/she? Are they a primary or secondary character and how do they
    relate to the game story?

  \item What do they look like? What are they wearing or carrying with them?

  \item What is their personality like and how does that personality help
    fulfill their role in the game story?

  \item How do they relate to other characters in the game?

  \item What are their strengths and weaknesses, and how can that affect the game story?

  \item What are the motivating character goals for this character?

\end{enumerate}

\subsubsection*{Dom Cobb}

The protagonist of the movie, a very skilled expert on information extraction
from sleeping target by infiltrating their subconscious.

He is tall with accurately combed hair and neat beard. Wearing suits in the form
of typical business attire and a wedding ring. Often has a gun in reality and
dreams.

Dom excels at everything he is doing and considered to be the best extractor,
though he has talent in architect area, as well as he performs well with
shooting and combat.

He was a gifted student of Mal's father with whom he became friends leading to
meeting his daughter, falling in love with and marrying her. They have two
children.

With Mal they experimented in deep dreams, resulting to spend nearly 50 years in
dream time, building own cities and feeling god---like. In this long dream Dom
convinced his wife that it was not real, they killed themselves and woke up, but
Mal continued to believe that it was not real and eventually has committed
suicide to ``wake up''. Before killing herself she has written a letter where
she blamed Dom in her death thus provoking him to follow her as the only way to
escape. Dom has become a fugitive and has plunged into a criminal world as a
professional extractor. He also has taken her spinner as a totem.

Arthur is the right hand for Dom. The two have met when Dom has joined the
criminal network. In the same area he has become acquinted with Eames.

Saito has been Dom's target but eventually turned into an employer and his way
to stop being a fugitive and reunite with his children.

Ariadne has joined Dom's team as an architect and is helping him during his
dream sessions with Mal's projection.

Dom's ultimate goal is to go back to his children and live happily together.

\subsubsection*{Mal Cobb}

Arguably the antagonist of the movie. She has dark curly hair and wears nice
dark-blue dress. Wearing a wedding ring and sometimes weapon. She used to have a
spinner as her totem.

She used to join Dom for shared dreaming resulting in her feeling that
everything is a dream and believing that she has to die to get away from this
``dream''.

In most of the movie time frames she has already committed a suicide.

Mal or Mal's projection often appears in Dom's dreams either to sabotage his
plans or to bring back the memory of their anniversary evening or children.

Her (her projection's) goal is to make Dom join her, that is, convince him to
kill himself.

The other part of protagonist forces is Robert's mind defenders who are trying
to stop the team from penetrating deeper in target's subconscious.

\subsubsection*{Setting Description}

The events happen in real world as well as in dream worlds.

We see a fast modern train, driving in a country-side area in some country,
presumably in Japan. Later we see the urban setting with character on the top of
the roof with helicopter landing spot.

The main character moves to the university in France with vast auditorium and
nice vintage setting. Later Dom and Adriane appear in a cosy cafe with typical
French streets of stone---block pavements, rows of fruit, vegetable and flower
stands.

Several shared dream sessions happen in what looks like abandoned warehouse with
big windows, scuffed walls and few columns.

Dom also appears in Mombasa where he meets Eames and Yusuf. We see narrow
streets with old houses and overcrowded cafe of very simple design.

We see different dream locations:

City under rain, hotel and hotel with no gravity, snow fortress and city which
Mal and Dom has built together.

\end{document}
