\documentclass{article}

\textheight = 600pt

\pagestyle{empty}

\begin{document}

\section*{Assignment 4: Assemble the Ideas}

\subsubsection*{Game Start}

We see a boat on a sandy shore with waves calming down. It is early morning, a
sailor is lying unconscious in the boat with soaked clothes and a dagger on his
side. He slowly comes to senses and it is now our task to help him find out what
has happened to him and why he was left on this grim island.

We begin with our main character stepping out of the boat on the sand and
observing the surroundings. There is a forest starting just some meters from the
shore, maybe around 30--40 meters. Behind waves are peacefully covering a
strand with low murmuring sound. As the sailor walks on the beach he starts to
hear obtuse animal noises coming out of the forest. He feels extremely thirsty
and on the edge of starvation. Now the player has a choice to go to the forest
to look for fruit and berries, hoping to find mushrooms or to investigate the
beach to find something useful, for example a lump of wood which could serve as
a club to defend against animals. Equipped with the dagger and club our main
character may feel more confident when walking to the forest.

When the sailor goes to the forest he might encounter various reptiles and
insects which he better avoid. He may as well drive away monkeys or other
animals in the pursue of fruits (fight with a monkey for bananas). If he meets
bigger beasts he should try to scare them off or fight for life.

After our character has gained enough energy and water the player continues
exploration and goes toward running water sound and eventually reaches the river
which fall into the sea and with a bridge. The sailor perceives that the island
might have a settlement with people and crosses the bridge to discover a path
leading into the island domain and going along with the river. He soon starts to
see some houses on the other side of the river and another bridge looming ahead.
The sailor decides to visit the village and after crossing the bridge he is
immediately taken by the guards. The people of the settlement look with
amazement while our hero is being brought to the central house where he is met
with the chieftain. The chieftain hears the story of our guy and agrees to help
him. From this point we shall be given numerous tasks of different type, meet
important people and carry on to accomplish the quests.

\end{document}
