\documentclass{article}

\textheight = 600pt

\pagestyle{empty}

\begin{document}

\section*{Assignment 3: Level Design}

The events of the game take place on a gloomy island with menacing mountain in
the middle. The island has forest filled with berries, fruit, mushrooms and
various animals. There is a river flowing across the island with its source
somewhere on the top of the mountain and falling into the sea surrounding the
land. Not very far from the shore there is an open space behind the forest and
that place was chosen by a small tribe who set up a small village in there. The
village is protected by fences, river and sea. The tribe has built two bridges
to pass over the humming torrent.

In the beginning of our game we see a sailor unconscious in a boat with soaked
clothes and a dagger on his side. He slowly comes to senses and its now our task
to help him find out what has happened to him and why he was left on this grim
island. He will move on the shore, exploring it, perhaps finding and taking a
club for further use. He may obtain various weapons and tools along the way.

The game is non-linear, the player might move to different areas in any order.
He will also be given several quests in the village by their people (e.g.,
fisherman asking to catch a rare fish in the river, hunter sending the sailor
back to the forest to skin a dangerous beast, shaman requiring certain plants
and flowers from the field and meadow and others) which he can do in any order
he prefers. The player usually moves by simple walking, though sometimes he
might be swimming or rowing a boat. The player might be given a pet (a dog,
maybe) in the village after earning certain reputation among its habitants. The
pet will later be helpful in the adventure.

The player will also have to solve different puzzles (e.g., how to cross the
boiling river near the waterfall to get to the cave entrance) and fight beasts
and unearthly creatures deep in the mountain. There are few secret places in the
game where the player might find gold coins, weapons, potions or armor.

For this assignment I am uploading two files: one is the .svg picture - the main
game levels design, and the other is a simple map design to give a general view
on how the areas might look like. The map does not contain a detailed plan for
the cave, only the entrance.

\end{document}
